Bounded Model Checking for Embedded Systems \\ (Position Paper)

### 2016-01-04 paper.tex
minor changes

Scratch is also another example of software model checker, which uses knowledge about the system to be verified and the underlying hardware, for detecting races related to direct memory access (DMA) for the Cell BE processor~\cite{Donaldson10}. The tool also uses BMC to detect DMA races, and bounded model checking with k-induction to prove absence of races.

@@

\bibitem{Rocha15}
Rocha H., Ismail H., Cordeiro L., Barreto R.:
\newblock {\em Model Checking Embedded C Software using k-Induction and Invariants.}
\newblock V Brazilian Symposium on Computing Systems Engineering (to appear), pp. 1--6, 2015.

\bibitem{Brain15}
Brain M., Joshi S., Kroening D., Schrammel P.:
\newblock {\em Safety Verification and Refutation by k-Invariants and k-Induction.}
\newblock In: International Symposium on Static Analysis, LNCS 9291, pp. 145--161, 2015.

>>>>

Scratch is also another example of software model checker, which uses knowledge about the system to be verified and the underlying hardware, for detecting races related to direct memory access (DMA) for the Cell BE processor~\cite{Donaldson10}. The tool also uses BMC to detect DMA races, and bounded model checking with \textit{k}-induction to prove absence of races.

@@

\bibitem{Rocha15}
Rocha H., Ismail H., Cordeiro L., Barreto R.:
\newblock {\em Model Checking Embedded C Software using \textit{k}-Induction and Invariants.}
\newblock V Brazilian Symposium on Computing Systems Engineering (to appear), pp. 1--6, 2015.

\bibitem{Brain15}
Brain M., Joshi S., Kroening D., Schrammel P.:
\newblock {\em Safety Verification and Refutation by k-Invariants and \textit{k}-Induction.}
\newblock In: International Symposium on Static Analysis, LNCS 9291, pp. 145--161, 2015.
